A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
each sentance on its own line for better diffs
added some text to the introduction (#31)
* added some text to the introduction

* each sentance on its own line for better diffs

* correct quotes

Co-authored-by: Aaron Peikert <aaron.peikert@posteo.de>

A cornerstone of scientific progress is the possibility to critically assess the validity of peer scientists’ scientific conclusions. Scientific claims should not be credible because of their originators' authority but by the transparency and replicability of their supporting evidence [@aac4716]. Enabling this assessment requires a systematic and rigorous approach to research.
<!-- define replicability and then... 
 define reproducibility -->
<!-- is a direct quote from my master thesis -->
<!-- I wouldn't want to cite it. @brandmaier, would you please rewrite? -->
A reproducible scientific product allows other researchers to obtain the same results from the same dataset in a way that enables substantive criticism and therefore facilitates replication.
<!-- lure the reader in -->
<!-- expand: who is calling it a requirement, maybe metascientific arguments-->
In fact, the the research community has long accepted reproducibility as an important element of “good scientific practice. <!-- examples missing --> However, ensuring reproducibility of computational analyses is still tedious and difficult, and there are still no widely accepted standards that can guide researchers when setting up their data analyses.  Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results. For example, @hardwicke2018 attempted to replicate open materials in the journal Cognition. Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required. For 13 articles, at least one outcome could not be reproduced — even with the original authors' assistance. @obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available. The authors could execute only 31 of the scripts without error and were able to reproduce the results of only 21 articles (within a reasonable period of time). Thus, there is a dire need to establish standards for reproducible workflows in order to move current research from just being transparent to becoming a cumulative computational knowledge acquisition process.

>>>>

A cornerstone of scientific progress is the possibility to critically assess the validity of peer scientists’ scientific conclusions.
Scientific claims should not be credible because of their originators' authority but by the transparency and replicability of their supporting evidence [@aac4716].
Enabling this assessment requires a systematic and rigorous approach to research.
<!-- define replicability and then... 
 define reproducibility -->
<!-- is a direct quote from my master thesis -->
<!-- I wouldn't want to cite it. @brandmaier, would you please rewrite? -->
A reproducible scientific product allows other researchers to obtain the same results from the same dataset in a way that enables substantive criticism and therefore facilitates replication.
<!-- lure the reader in -->
<!-- expand: who is calling it a requirement, maybe metascientific arguments-->
In fact, the the research community has long accepted reproducibility as an important element of "good scientific practice." <!-- examples missing -->
However, ensuring reproducibility of computational analyses is still tedious and difficult, and there are still no widely accepted standards that can guide researchers when setting up their data analyses.
Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results.
For example, @hardwicke2018 attempted to replicate open materials in the journal Cognition. Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced — even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and were able to reproduce the results of only 21 articles (within a reasonable period of time).
Thus, there is a dire need to establish standards for reproducible workflows in order to move current research from just being transparent to becoming a cumulative computational knowledge acquisition process.
